SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-07-27 scipy-1.0/paper.tex
Third round of revisions based on reviewer feedback in manuscript PR 43.

Over the last three years our sparse matrix handling internals have
been rewritten and performance has been improved. Iterating over 
and slicing of CSC and CSR matrices is now faster by up to 35\%,
and the CSR to COO matrix format conversion is now several times faster.
COO matrices are now generally more memory efficient. Importantly,
SuperLU\cite{superlu_ug99} was updated to version 5.2.1, enhancing
the low-level implementations leveraged by a subset of our \texttt{sparse}
offerings.

From a new features standpoint, \texttt{scipy.sparse} matrices and linear
operators now support the Python matrix multiplication (@) operator when
available. We've added \texttt{scipy.sparse.norm} and \texttt{scipy.sparse.random} 
for computing sparse matrix norms and drawing random variates from arbitrary 
distributions, respectively. Also, we've made a concerted effort to bring the
\texttt{scipy.sparse} API into line with the equivalent NumPy API where possible,
typically by adding support for kwargs like axis=None or copy=False to many methods.

>>>>

Over the last three years our sparse matrix handling internals have
been rewritten and performance has been improved. Iterating over 
and slicing of CSC and CSR matrices is now faster by up to 35\%,
and the CSR to COO matrix format conversion is now several times faster.
Importantly, SuperLU\cite{superlu_ug99} was updated to version 5.2.1, enhancing
the low-level implementations leveraged by a subset of our \texttt{sparse}
offerings.

From a new features standpoint, \texttt{scipy.sparse} matrices and linear
operators now support the Python matrix multiplication (@) operator when
available. We've added \texttt{scipy.sparse.norm} and \texttt{scipy.sparse.random} 
for computing sparse matrix norms and drawing random variates from arbitrary 
distributions, respectively. Also, we've made a concerted effort to bring the
\texttt{scipy.sparse} API into line with the equivalent NumPy API where possible,
typically by adding support for kwargs like \texttt{axis=None} or
\texttt{copy=False} to many methods.
